A new form of transcorrelated Hamiltonian inspired by range-separated DFT

### 2021-02-26 cusp_j/paper/revised/paper.tex
modified Yuan plugins

An alternative point of view using a {correlation} factor is the so-called transcorrelated (TC) approach where the full effect of the {correlation} factor is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the {correlation} factor. 
{As the TC theory does not use an orthogonal projector with the basis set as in F12 theory, the correlation factor in the TC theory is often referred to as a Jastrow factor.} 
Seminal equations were derived by Hirschfelder\cite{Hirschfelder-JCP-63} who obtained an effective non hermitian operator based on a specific form of Jastrow factor, and later on Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHanLin-2-PRSLA-69} derived the equations of the TC Hamiltonian for a general exponential form of the Jastrow factor which insures size extensivity. 
The obtained TC Hamiltonian contains certain new features with respect to the usual Hamiltonian: the TC Hamiltonian contains an additional effective two- and three-electron scalar potential together with is a non hermitian two-electron differential operator. Because of its non-hermitian nature, the TC Hamiltonian looses the variational principle, and Boys and Handy managed to derive equations to optimize both orbitals and Jastrow parameters for a single Slater determinant. 
Nevertheless, such a constrained form for the Slater part of the wave function together with the loose of variational principle makes it difficult to find a monotonic convergence of computed energies\cite{Handy-MolPhys-71}.

>>>>

An alternative point of view using a {correlation} factor is the so-called transcorrelated (TC) approach where the full effect of the {correlation} factor is incorporated into the calculation through a similarity transformation of the original Hamiltonian by the {correlation} factor. 
{As the TC theory does not use an orthogonal projector with the basis set as in F12 theory, the correlation factor in the TC theory is often referred to as a Jastrow factor.} 
Seminal equations were derived by Hirschfelder\cite{Hirschfelder-JCP-63} who obtained an effective non hermitian operator based on a specific form of Jastrow factor, and later on Boys, Handy and co-workers\cite{BoyHan-PRSLA-69,BoyHanLin-1-PRSLA-69,BoyHan-2-PRSLA-69} derived the equations of the TC Hamiltonian for a general exponential form of the Jastrow factor which insures size extensivity. 
The obtained TC Hamiltonian contains certain new features with respect to the usual Hamiltonian: the TC Hamiltonian contains an additional effective two- and three-electron scalar potential together with is a non hermitian two-electron differential operator. Because of its non-hermitian nature, the TC Hamiltonian looses the variational principle, and Boys and Handy managed to derive equations to optimize both orbitals and Jastrow parameters for a single Slater determinant. 
Nevertheless, such a constrained form for the Slater part of the wave function together with the loose of variational principle makes it difficult to find a monotonic convergence of computed energies\cite{Handy-MolPhys-71}.
